Laplacian envelope

### 2021-09-06 Notes/laplace.tex
sign of hessian

To write down the Hessian, we will first define some notation.
We define the matrix \(\mathbf{X}(s) = \fund(0) \enc \fund(s)\).
Given a four-index array \(H_{ijkl}\), we define \(H\trans_{ijkl} = H_{klij}\).
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{alignedat}{2}
    R_{ijkl} &= \smash{\pdiff{\hat{A}}{\frgm_{ij} \circ ; \frgm_{kl}}} &
    &=
    \eqm_i \brc{\fundm_{ik}(0) - \fundm_{jk}(0)} \brc{\thbm_k(s) - \thbm_l(s)} \\
    &&&\hphantom{=} {}
    + \eqm_i \brc{{X}_{ik}(s) - {X}_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)} \\
    &&& \hphantom{=} {}
    + \eqm_i {c}_i(s) \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)},  \\
  S_{ijkl} &= \smash{\pdiff{\hat{A}}{\encm_{ij} ; \frgm_{kl}} } &
  &= \eqm_k \brc{\fundm_{ki}(0) - \fundm_{li}(0)} \brc{\etwm_i(s) - \etwm_j(s)} \\
    &&& \hphantom{=} {}
    + \eqm_i \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} \brc{\etwm_k(s) - \etwm_l(s)},
\end{alignedat}
\end{equation}
%
where \(R\) contains only those terms where \( \frgm_{ij} \) precedes \( \frgm_{kl} \) in the matrix products from the expression for \( \hat{A} \) in \cref{eq:larea}.
The missing terms sum to \(R\trans\).

@@

Note that
%
\begin{equation}\label{eq:etafund}
  \etw(s) = \text{const.} - \fund(s)\w.
\end{equation}
%
As we are only interested in differences of the \(\etwm_i(s)\), we can drop the constant.
Then
%
\begin{equation}\label{eq:etarecur}
  -(s\I + \ onev \arow - \frg)\etw(s) = \w.
\end{equation}
%
We can then write
%
\begin{equation}\label{eq:detarecur}
  \etw(s) = -\frac{(\arow \etw(s)) \onev + \w}{s} + \delta \etw(s),
  \qquad
  (\frg - s\I) \delta \etw(s) = \frac{\frg \w}{s}.
\end{equation}
%
As we are only interested in differences, we can drop any terms proportional to \(\onev\) in \(\etw(s)\).

>>>>

To write down the Hessian, we will first define some notation.
We define the matrix \(\mathbf{X}(s) = \fund(0) \enc \fund(s)\).
Given a four-index array \(H_{ijkl}\), we define \(H\trans_{ijkl} = H_{klij}\).
Then we denote
%
\begin{equation}\label{eq:hessparts}
\begin{alignedat}{2}
  R_{ijkl} &= \smash{\pdiff{\hat{A}}{\frgm_{ij} \circ ; \frgm_{kl}}} &
  &=
    - \eqm_i \brc{\fundm_{ik}(0) - \fundm_{jk}(0)} \brc{\thbm_k(s) - \thbm_l(s)} \\
  &&&\hphantom{=} {}
    - \eqm_i \brc{{X}_{ik}(s) - {X}_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)} \\
  &&& \hphantom{=} {}
    - \eqm_i {c}_i(s) \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} 
          \brc{\etwm_k(s) - \etwm_l(s)},  \\
  S_{ijkl} &= \smash{\pdiff{\hat{A}}{\encm_{ij} ; \frgm_{kl}} } &
  &= 
    - \eqm_k \brc{\fundm_{ki}(0) - \fundm_{li}(0)} \brc{\etwm_i(s) - \etwm_j(s)} \\
  &&& \hphantom{=} {}
    - \eqm_i \brc{\fundm_{ik}(s) - \fundm_{jk}(s)} \brc{\etwm_k(s) - \etwm_l(s)},
\end{alignedat}
\end{equation}
%
where \(R\) contains only those terms where \( \frgm_{ij} \) precedes \( \frgm_{kl} \) in the matrix products from the expression for \( \hat{A} \) in \cref{eq:larea}.
The missing terms sum to \(R\trans\).

@@

Note that
%
\begin{equation}\label{eq:etafund}
  \etw(s) = \text{const.} - \fund(s)\w.
\end{equation}
%
As we are only interested in differences of the \(\etwm_i(s)\), we can drop the constant.
Then
%
\begin{equation}\label{eq:etarecur}
  -(s\I + \onev \arow - \frg)\etw(s) = \w.
\end{equation}
%
We can then write
%
\begin{equation}\label{eq:detarecur}
  \etw(s) = -\frac{(\arow \etw(s)) \onev + \w}{s} + \delta \etw(s),
  \qquad
  (\frg - s\I) \delta \etw(s) = \frac{\frg \w}{s}.
\end{equation}
%
As we are only interested in differences, we can drop any terms proportional to \(\onev\) in \(\etw(s)\).
